A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2020-01-29 0_reviewer_response.tex

\Que{Example text by reviewer.}
\Ans{Example response.}
\paper{New section name}{
Remaining text, followed by 
\revise{outdated text in manuscript}{new text in manuscript}
\revisepar{
Old paragraph which might contain various i.e. multiple lines, which makes the LaTeX macro for strikout text fail, because the soul package doesn't work well enough for our purposes.
}
{Revised paragraph is better.}
}
%\todo{Comment for us internally (should be removed before this letter is sent).}
\commits{123commit-hash}

\section{Reviewer 1}
\Summary{
Overall, the paper proposes some novel frameworks which are meaningful to additive manufacturing. Therefore, I suggest it for publication once the following major comments are addressed. 
}
\Ans{
Thank you.
We have addressed the comments, and have clarified our contributions.
}

%\stepcounter{question}
\Que{
Could the authors provide a mathematical foundation for the relationship between the underfill/overfill areas and the allowed variation of bead width?
I believe the proposed beading scheme can reduce the underfill/overfill areas somehow.
But we still lack a mathematical theory to guide the design.
}
\Ans{
The relationship between under-/overfill and bead widths can be split into several components:
\begin{enumerate*}
\item depending on the feature size
\item depending on the change in feature size
\item depending on the topology
\end{enumerate*}
.
In the first case we consider a part with a constant feature size, in the second we consider the rate of change of feature size and in the third we consider the influence of 3-way intersections.

1. When considering a part with constant feature diameter $d$ we note that the beading only depends on the feature diameter: $B(n, r) = B(q(2r), r)$.
From the beading function we can easily derive the under-/overfill by summing over the bead widths $W$.
We can then derive that the naive scheme produces over-/underfill at all diameters except $d=2i w^*$, the centered scheme for $(i + 0.8) w^* < d < (i+ 1.25) w^*$ and the constant and distributed schemes nowhere (except for features smaller than $w^*$).
We have added a paragraph to the new section~5.1~Theoretical consideration to explain this and the implications for design for additive manufacturing.

@@

2. When the feature size changes the amount of over-/underfill is related to a bisector angle $\alpha < \alpha_\text{max}$ according to the formula already given in section~3.3, paragraph `Significance measure': 
``This corresponds to overfill areas and underfill areas the size of \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$}''.
This formula is also relevant for the other beading schemes because the nonsignificant regions are filled in a similar fashion to the naive technique.
For small bisector angles these under-/overfill areas are considered to be permittably small.
We hope that this explanation suffices for the reviewer and the existing text suffices for the general reader.

3. The topology also has an influence on underfill. For example, a 3-way intersection in a 3D model which is a honeycomb pattern with a feature diameter of $w^*$ causes some over and underfill using \emph{any} possible technique, because 3 printed beads come together in the same point.
Also a honeycomb of $2w^*$ diameter causes some underfill in the center;
when 3 beads surround a single point there will always remain a micro-gap because of the high viscosity of the molten filament.
This is handled in Fig.~12 and the last paragraph of section~3.6.

As for `the allowed variation of bead width': our vision \emph{was} that there should be no binary criterion for manufacturability and instead there should only be a floating number evaluation of manufacturability of a given bead width.
However, we have now put bounds on the induced bead widths, so that the reader could compare our method to any range of `allowed variation' according to any manufacturability criterion.
See the answer to question 3.4.
}

\commits{
2e1c40be93f92a8495c0d7fa379e983dd3ee7b98 % emphasize implication for DfAM in conclusion
5b8c5971d606089754ba118560e51ec6d7dfda0b % new section~`Theoretical considerations'
7c2224fc713f5b68436f432a1ade506e9dacf500 % lil edit in above section
420cf6886a8e248aec4aafc04d13abc693da8dd0 % fix for naive over-/underfill area formula
86cd8dd7f2112696f650736a81b24b63af739639 % lil typo
}
\paper{3.3 Method, Significance measure}{
This corresponds to overfill areas and underfill areas the size of \\ \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$
}
\paper{5.3 Limitations, first paragraph}{
\revise{}{
Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
For the center\revise{ed} scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
where $w_\text{min}$ is a configurable parameter when using the widening meta-scheme.
}
}
\paper{6. Conclusion, last paragraph}{
\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
}

### 2020-01-29 8_discussion.tex
center scheme => centered scheme

\revise{}
{
\subsection{Limitations}
Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
For the center scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
where $w_\text{min}$ is a configurable parameter when using the widening meta-scheme.

>>>>

\revise{}
{
\subsection{Limitations}
Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
For the center\revise{ed} scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.25) w^*$ in order to avoid underfill.
For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
where $w_\text{min}$ is a configurable parameter when using the widening meta-scheme.
